A Hybrid Neutronics Method for Time-Dependent Control Rod Modeling in Molten Salt Reactors

### 2024-09-11 acros.tex
saaf sn method
sn terms
add verification chapter for referencing, hybrid chapter edits
turbulence verification section

@@

@@

\newacronym{DNS}{DNS}{Direct numerical simulation}

@@

@@

@@

\newacronym{INS}{INS}{incompressible Navier-Stokes}

@@

@@

\newacronym{OOP}{OOP}{Object-oriented programming}

@@

@@

>>>>

\newacronym{BFS}{BFS}{backward-facing step}

@@

\newacronym{CMFD}{CMFD}{coarse-mesh finite difference}

@@

\newacronym{DNS}{DNS}{direct numerical simulation}

@@

\newacronym{GMRES}{GMRES}{generalized minimal residual}

@@

\newacronym{HOLO}{HOLO}{high-order/low-order}

@@

\newacronym{INS}{INS}{Incompressible Navier-Stokes}
\newacronym{INSAD}{INSAD}{Incompressible Navier-Stokes Automatic Differentiation}

@@

\newacronym{NASA}{NASA}{National Aeronautics and Space Administration}
\newacronym{NDA}{NDA}{nonlinear diffusion acceleration}

@@

\newacronym{OOP}{OOP}{object-oriented programming}

@@

\newacronym{PJFNK}{PJFNK}{preconditioned Jacobian-free Newton-Krylov}

@@

\newacronym{SA}{SA}{Spalart-Allmaras}
\newacronym{SAAF}{SAAF}{self-adjoint angular flux}
